	\pagenumbering{roman}
		\addcontentsline{toc}{section}{Certificate of Approval}
		\large
			\chapter*{Certificate of Approval}
		\normalsize 
		    This is to certify that the project entitled \textbf{“StudyBug”} submitted by Anjana Silinchhe Shrestha, Pradipta Joshi, Prasant Rai and Sushma Shrestha to the \textbf{Department of Computer Engineering} as a \textbf{group project}, in partial fullfillment of the requirements for the award of the degree/course in Computer Engineering. The project was carried out under special supervision and within the time frame prescribed by the syllabus. \\ 
		    \\
			We found the students to be hardworking, skilled, bona fide and ready to undertake any commercial and industrial work related to their field of study and hence we recommend the award of Bachelor of Computer Engineering degree. \\
			\vspace{2cm} \\
			.............................................\\
			Er. Dinesh Gothe\\
			Head of Department \\
			Department of Computer Engineering, KhCE\\
            \vspace{1cm}\\
            .............................................\\
			Er. Sunil Banmala\\
			Supervisor \\
			Department of Computer Engineering, KhCE\\
            \vspace{1cm}\\
            .............................................\\
			Er. Ramesh Prajapati\\
			Supervisor \\
			Department of Computer Engineering, KhCE\\
		\break



		\addcontentsline{toc}{section}{Copyright}
		\large
			\chapter*{Copyright}
		\normalsize
			The author has agreed that the library, Khwopa College of Engineering  may make this report freely available for inspection. Moreover, the author has agreed that permission for the extensive copying of this project report for scholarly purpose may be granted by supervisor who supervised the project work recorded here in or, in absence the Head of The Department where in the project report was done. It is understood that the recognition will be given to the author of the report and to Department of Computer Engineering, KhCE in any use of the material of this project report. Copying or publication or other use of this report for financial gain without approval of the department and author’s written permission is prohibited. Request for the permission to copy or to make any other use of material in this report in whole or in part should be addressed to: \\
			\vspace{1cm} \\
			Head of Department \\
			Department of Computer Engineering\\
			Khwopa College of Engineering\\
			Liwali,\\
			Bhaktapur, Nepal\\
		\break

	
	    \addcontentsline{toc}{section}{Acknowledgement}
		\large
			\chapter*{Acknowledgement}
		\normalsize
			We take this opportunity to express our deepest and sincere gratitude to our HoD Er. Dinesh Gothe, for his insightful advice, motivating suggestions for this project and also for his constant encouragement and advice throughout our Bachelor’s program.
			\\We are deeply indebted to our Supervisor Er. Sunil Banmala for boosting our efforts and moral by his valuable advises and suggestion regarding the project, giving us realization of the practical scenario of the project and supporting us in tackling various difficulties.\\
			\vspace{1cm}

			\begin{tabular}{p{2in}p{3in}}
    			Anjana Silinchhe Shrestha & KCE074BCT004\\
    			Pradipta Joshi & KCE074BCT021\\
    			Prasant Rai & KCE074BCT024\\
    			Sushma Shrestha & KCE074BCT043\\
    		 \vspace{0.3in}
    		\end{tabular}
		\break
		
		\addcontentsline{toc}{section}{Abstract}
		\large
			\chapter*{Abstract}
		\normalsize
		StudyBug is a web-based aesthetic study platform developed to address common challenges faced by students such as lack of focus, poor time management, and inconsistent study habits. The system integrates essential study-support features including task management, study scheduling, focus timers, and progress tracking within a single, user-friendly interface. Special emphasis is placed on aesthetic design to create a calm and engaging study environment that reduces distractions and increases motivation. The website is fully responsive and accessible across both desktop and mobile devices, allowing users to study flexibly. By combining productivity tools with thoughtful UI/UX design, StudyBug aims to improve study consistency, enhance concentration, and support effective learning practices.

		\textbf{Keywords}:\textit{Study website, Focus timer, Study planning, Task management, Aesthetic UI, Student productivity}

		\break

		\addcontentsline{toc}{section}{Contents}
		\tableofcontents
		
		% \addcontentsline{toc}{section}{List of Tables}
		% \listoftables
		\break
		\pagebreak

		\addcontentsline{toc}{section}{List of Figures}
		\listoffigures
		\break
	
	
	
		\addcontentsline{toc}{section}{List of Symbols and Abbreviation}
		\Large
			\begingroup
				\let\clearpage\relax
				\chapter*{List of Abbreviation}
			\endgroup
		    \normalsize
			\begin{table}[h]
				\begin{center}
					\begin{tabular}{l l}
						\textbf{Abbreviations} & \textbf{Meaning} \\
\textbf{UI}   & User Interface \\
\textbf{UX}   & User Experience \\
\textbf{MVP}  & Minimum Viable Product \\
\textbf{DFD}  & Data Flow Diagram \\
\textbf{API}  & Application Programming Interface \\
\textbf{HTML} & HyperText Markup Language \\
\textbf{CSS}  & Cascading Style Sheets \\
\textbf{JS}   & JavaScript \\
\textbf{OAuth} & Open Authorization \\
\textbf{CRUD} & Create, Read, Update, Delete \\
					\end{tabular}
				\end{center}
			\end{table}
		\break
		\pagebreak
		
	